---
title: "project 467"
output:
  pdf_document: default
  html_document: default
---
load packages
```{r}
library(tidyverse)
library(caret)
library(MuMIn)
```

load data file
```{r}
df <- read.csv("C:/Users/Lynn/Desktop/DATA 467/diamond_quality.csv", header = TRUE)
```
1. Summary of all the variable
Null -> not factor variable
```{r}
glimpse(df)
sapply(df[sapply(df, class) == "character"], unique)
diamond <- df %>% mutate_if(is.character, as.factor)
diamond$Carat.Size <- df$ï..Carat.Size
diamond <- diamond[, -1]
glimpse(diamond)
```
2. Multiple linear regression model 
5%
```{r}
whole_regression <- lm(Price~., data = diamond)
reduced_regression <-  lm(Price~Carat.Size+Cut+Depth+Clarity+Color, data = diamond)
extra_reduced_regression <- lm(Price~Carat.Size+Cut+Clarity+Color, data = diamond)
summary(whole_regression)
summary(reduced_regression)
summary(extra_reduced_regression)
```
Report, Table

3. comparing between models.
```{r}
anova(whole_regression, reduced_regression)
```
H0: all Bi = 0
HA: at least 1 Bi != 0
Bi is the slope of each variable that we leave out.
p val >5% ==> fail to reject H0==> those left out variables are not significant. The reduced model is better than the full model.
```{r}
anova(extra_reduced_regression, whole_regression)
```


pval<5% ==> Not enough evidence to state that Depth is a significant predictor.




4. BAckward criterion
```{r}
n = length(resid(whole_regression))
diamond_back_bic = step(whole_regression, distraction = "backward", k = log(n))
```
THis indicates that the reduced model that we made is correct.
5. Inference
```{r}
plot(Price~Color,diamond)
plot(Price~Clarity, diamond)
plot(Price~Depth, diamond)
plot(Price~Cut, diamond)
plot(Price~Carat.Size, diamond)
plot(Price~Table,diamond)
plot(Price~Report, diamond)

```

** Check if Depth is a significant predictor for Price.
```{r}
DvsP <- lm(Price~Depth, diamond)
summary(DvsP)
null <- lm(Price~1, diamond)
anova(null, DvsP)
```
Depth is not a significant predictor.
pvalue is too larger ==> not efficient. Depth is insignificant. the model with depth is not different from the null model.

** Check if Cut is a significant predictor for price
```{r}
CvsP <- lm(Price~Cut, diamond)
anova(CvsP)
```
==> not affect the Price that much.

** Check of Color is significant predictor.
```{r}
ColorvsP <- lm(Price~ Color, diamond)
anova(ColorvsP)
```
==> very effective 

** Check of Clarity is significant predictor.
```{r}
ClarityvsP <- lm(Price~ Clarity, diamond)
anova(ClarityvsP)
```
==> significant

**CHeck if Carat Size is significant
```{r}
SizevsP <- lm(Price~ Carat.Size, diamond)
anova(SizevsP)
cor(diamond$Price, diamond$Carat.Size)
```

** Check if Table is significant predictor for price
```{r}
Tablevsp <- lm(Price~Table, diamond)
summary(Tablevsp)
```

** Check if Report is significant predictor for Price
```{r}
RvsP <- lm(Price~Report, diamond)
anova(RvsP)
```
```{r}
summary(reduced_regression)$coefficients
```

6. WEight
```{r}
summary(reduced_regression)
unique(diamond$Color)
unique(diamond$Cut)
unique(diamond$Clarity)
```






